\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
edits through the end of the paper

The experiment simulates one hour of traffic in two cities: a
9$\times$11km$^{2}$ slice of downtown Austin, Texas\footnote{bounded by the
Mopac and Springdale Road horizontally, and Oltorf Street and Koenig Lane
vertically}, and a 15$\times$13km$^{2}$ slice of downtown Houston, Texas
\footnote{bounded by Ella Boulevard and Eastex Freeway horizontally, and West
Alabama Street and Crosstimbers Street vertically}.  The step duration is fixed
at 0.1 seconds. While the intersection policies vary, the agents spawned and
their routes remain the same.  A generator creates one new agent every 1
simulation second, with a uniformly random starting position and goal.

These experiments are deterministically reproducible. A seed for the
pseudo-random number generator, the input graph, and the generators'
configuration fully determine the outcome of any simulation \footnote{This
determinism may break down when generators use worker threads, since routes
may be computed in different orders, causing agents to enter the road at
different times.}. After setting up a scenario in the UI, users can save this
configuration for resimulation.

The speed of simulation depends on the step duration dt, the map size, and the
number of agents. A measure independent of these factors is the number of agent
steps per second. On a 2.4 GHz machine, this can be observed to average at about
150,000, a number comparable to existing simulators \cite{SUMOthesis}. When dt
= 0.1 seconds, this means 15,000 agents can be comfortably simulated in
real-time. Further optimizations are planned.

@@

This paper has presented AORTA, a new city-scale traffic simulation framework
that focuses on configurability. In conjunction with Open Street Maps, AORTA
allows users to repeat an experiment in different places with minimal effort.
Future work will exploit the flexible infrastructure of interactions between
agent behaviors and intersections by exploring dynamic replanning and adaptable
signal timings. On top of these structures, applications could experiment with
ideas such dynamic contra-flow \cite{ITSC11-hausknecht}.  There will also be an
effort to improve AORTA as a framework by including a lane-changing model,
preventing gridlock, and supporting the resources of supercomputing clusters.

AORTA's map construction process, although flexible, cannot completely account
for incompletedness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns at
each intersection often misses common features like right turn-only lanes and
shared center left turn lanes. There are many circumstances where AORTA
simulates one intersection as several in close proximity because roads do not
geometrically line up, but functionally they do.  If OSM encoded this data, the
performance of intersection policies and the realism of the simulation would
improve. Other simulators have identified similar issues before
\cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

\commentd{Er, so how do I finally end this?}

\addtolength{\textheight}{-12cm}  % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

>>>>

The experiment simulates one hour of traffic in two cities: a
9$\times$11km$^{2}$ slice of downtown Austin, Texas\footnote{bounded by the
Mopac, Springdale Road, Oltorf Street and Koenig Lane}, and a
15$\times$13km$^{2}$ slice of downtown Houston, Texas\footnote{bounded by Ella
Boulevard, Eastex Freeway, West Alabama Street and Crosstimbers Street}.  The
step duration is fixed at 0.1 seconds. While the intersection policies vary,
the agents spawned and their routes remain the same.  A generator creates one
new agent every 1 simulation second, with a uniformly random starting position
and goal.

These experiments are deterministically reproducible. A seed for the
pseudo-random number generator, the input graph, and the generators'
configuration fully determine the outcome of any simulation \footnote{This
determinism may break down when generators use worker threads, since routes
may be computed in different orders, causing agents to enter the road at
different times.}. After setting up a scenario in the UI, users can save this
configuration for re-simulation.

The speed of simulation depends on the step duration dt, the map size, and the
number of agents. A measure independent of these factors is the number of agent
steps per second. On a 2.4 GHz machine, this can be observed to average at
about 150,000, a number comparable to existing simulators \cite{SUMOthesis}.
When the time step is 0.1 seconds, this means 15,000 agents can be comfortably
simulated in real-time. Further optimizations are planned.

@@

This paper has presented AORTA, a new city-scale traffic simulation framework
that focuses on configurability. In conjunction with Open Street Maps, AORTA
allows users to repeat an experiment in different places with minimal effort.
Future work will exploit the flexible infrastructure of interactions between
agent behaviors and intersections by exploring dynamic replanning and adaptable
signal timings. On top of these structures, applications could experiment with
ideas such dynamic contra-flow \cite{ITSC11-hausknecht}.  There will also be an
effort to improve AORTA as a framework by including a lane-changing model,
preventing gridlock, and supporting more agents through parallel computing.

AORTA's map construction process, although flexible, cannot completely account
for incompleteness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns at
each intersection often misses common features like right turn-only lanes and
shared center left turn lanes. There are many circumstances where AORTA
simulates one intersection as several in close proximity because roads do not
geometrically line up, but functionally they do.  If OSM encoded this data, the
performance of intersection policies and the realism of the simulation would
improve. Other simulators have identified similar issues before
\cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

% \addtolength{\textheight}{-12cm}  % This command serves to balance the column lengths
%                                   % on the last page of the document manually. It shortens
%                                   % the textheight of the last page by a suitable amount.
%                                   % This command does not take effect until the next page
%                                   % so it should come on the page before the last. Make
%                                   % sure that you do not shorten the textheight too much.
